% Editable technical prose used by the regression documents.
% It intentionally contains no generated filler or lipsum text.
\newcommand\WBTextA{%
A two-column output routine does not build both columns at the same time. TeX first contributes paragraphs, displays, insertions, and penalties to a vertical list. When that list reaches the current column goal, the output routine stores the completed left column and starts collecting the right column. This sequencing is the central difficulty for an inline full-width equation: a request seen in the left column can still influence the right-column height, while a request first seen in the right column is already too late to reshape the stored left column.\par
The prototype therefore leaves ordinary paragraph construction unchanged and records a narrow marker in the vertical list. During page assembly, the marker position is measured from the top of the packaged column. Both columns can then be divided at a common vertical coordinate, and the wide material can be inserted between the upper and lower fragments without invoking \texttt{\string\onecolumn} or balancing the preceding text.\par}

\newcommand\WBTextB{%
The reservation must include the natural height and depth of the captured equation, the external separation above and below the band, and any decorative rules belonging to the band itself. Measuring these values before the marker is emitted prevents a late change in the equation box from invalidating the reserved gap. A production implementation should also record a request identifier so that several pending equations cannot overwrite a single global box.\par
Page breaking remains conservative. When the remaining column space is smaller than the reservation, the package forces a column transition. If the marker eventually lands in the right column, the current page is shipped without the band and the saved equation is moved to the top of the following page. This fallback is less ambitious than arbitrary repagination, but it protects text from overlap and loss.\par}

\newcommand\WBTextC{%
Footnotes and floats are harder than ordinary paragraphs because they are managed through insertion registers and deferred lists. Their source location does not always match the box in which they are finally placed. For this reason, the current package reports pending single-column and double-column floats instead of claiming compatibility. The regression documents include simple footnotes and float requests so that future changes reveal lost insertions, duplicated material, or altered ordering.\par
Hyperlinks require a separate check. An equation number may be correct while its destination anchor points to the top of the page or to the original marker position. A useful test must compile twice, resolve the reference, and inspect the destination visually or with a PDF object tool. Tagged PDF introduces a larger structural problem because visual box surgery can produce a reading order different from the source order.\par}

\newcommand\WBTextD{%
The asymmetric rules make a wide equation easier to distinguish from surrounding prose without enclosing it in a heavy frame. The upper rule begins at the left edge and spans a configurable fraction of the text width. The lower rule spans the same fraction but terminates at the right edge. Their thickness, length fraction, and distance from the equation can be changed independently, and the decoration can be disabled for journals that require plain mathematics.\par
The rules are included inside the measured band box. Consequently, changing the rule thickness or separation changes the reservation automatically. This is safer than drawing the rules later as an overlay, because an overlay could collide with text even though the equation itself fitted inside the reserved region.\par}

\newcommand\WBTextE{%
A reliable page-boundary check must distinguish the declared dimensions of a box from the natural dimensions of its contents. Packing an overfull list into a box of the requested height does not remove the excess nodes; they can protrude below the nominal box and appear outside the text area. The hardened implementation asks Lua to return the natural height of the post-marker material. If it is greater than the available lower-column region, the band is deferred instead of concealing the overflow in an exact-height box.\par
Rendered-page inspection is still necessary. Compilation success only proves that TeX produced a PDF. It does not prove that the text stayed inside the type area, that the two lower columns begin at the same visual position, or that rules align with the intended edges. The test runner therefore compiles each document twice and a separate bounds checker examines the resulting page geometry.\par}

\newcommand\WBTextF{%
Column depth differences can arise from displayed mathematics, headings, lists, or a final line with unusual glyph depth. The assembly code uses top-aligned lower fragments and normalizes the declared height of each column fragment before placing them in a shared horizontal row. This keeps their starting baselines aligned while allowing the columns to end at different positions, as ordinary unbalanced two-column pages do.\par
A final page is not automatically balanced by the standard article class. It is therefore normal for the left column to contain more text than the right column. The important invariant is that neither column extends below the configured text height. Tests should not mistake an intentionally ragged final page for a clipping defect.\par}

\newcommand\WBTextG{%
The implementation intentionally supports only one pending band. If another environment closes before the first saved band is shipped, the new request is rejected with a package error rather than silently replacing the earlier equation. Queue support would require a unique marker and saved box for every request, together with a policy for two bands that compete for the same page. Rejecting the second request is restrictive, but it makes the present behavior deterministic.\par
Compatibility with classes such as REVTeX and IEEEtran cannot be inferred from success with the standard article class. Those classes own substantial output-routine logic for floats, balancing, and publication-specific marks. A future package should provide class adapters or use documented output hooks when the required information becomes available there.\par}

\newcommand\WBTextH{%
The most useful acceptance test compares three layouts generated from identical prose and mathematics. A naive switch to one-column mode demonstrates the unwanted page flush. A \texttt{strip} environment demonstrates the closest established technique. The new environment should preserve the ordinary two-column page, insert the equation at the requested vertical region when safe, and continue text below the reservation without balancing the material above it.\par
These comparisons should use meaningful paragraphs because realistic punctuation, inline code, equations, headings, and footnotes produce line-breaking patterns that synthetic filler may not expose. The source files in this package are designed to be edited directly so that longer equations and journal-specific dimensions can be tried without first replacing placeholder text.\par}
